Reasoning about a Capability Machine with Local Capabilities

### 2017-06-13 popl-2018/paper.tex
added a bit of text pointing out macros make examples small and readable

\subsubsection{Future worlds}
The future world relations model how memory may evolve over time. The
\emph{public future world} $W' \futurewk W$ requires that $\dom(W') \supseteq
\dom(W)$ and $\forall r \in \dom(W) \ldotp W'(r) \futurewk W(r)$. That is, in a
public future world, new regions may have been allocated, and existing regions
may have evolved according to the public future region relation (defined below).
The \emph{private future world} relation $W' \futurestr W$ is defined similarly,
using a private future region relation.

@@

Notice that the public future region relation is a subset of the
private future region relation.

@@

\section{Examples}
\label{sec:examples}
In this section, we demonstrate how our formalization of capability safety
allows us to prove local-state encapsulation and control-flow correctness
properties for challenging program examples. The security measures of
Section~\ref{sec:stack-and-return-pointer} are deployed to ensure these
properties. Since we are dealing with assembly language, there are many details
to the formal treatment, and therefore we necessarily have to omit some details
in the lemmas we state here. The interested reader can find all the technical
details in the technical appendix~\citep{technical_appendix}.

@@

For our purposes, this restriction is unproblematic, since we are only
interested in proving semantic properties (e.g., an assertion will never fail).
However, in other situations, we may be interested in proving more syntactic
properties like the more syntactic properties, that are often considered in
object capability literature like confinement, no authority amplification etc.
Although such properties are typically more restrictive and less easy to use for
reasoning, \cite{Devriese:2016ObjCap} have demonstrated how a logical relation
much like ours can be adapted to also support them, by quantifying the logical
relation over a custom interpretation of effectful computations and the type of
references. We expect their solution can be readily adapted to our setting,
modulo some details (like the fact that we do not just have read-write
capabilities, but also other types).

% \emph{No program logic} TODO: discuss this? 
\\\\

>>>>

\subsubsection{Future worlds}
\label{subsec:future-worlds} 
The future world relations model how memory may evolve over time. 
The \emph{public future world} $W' \futurewk W$ requires that $\dom(W') \supseteq
\dom(W)$ and $\forall r \in \dom(W) \ldotp W'(r) \futurewk W(r)$. That is, in a
public future world, new regions may have been allocated, and existing regions
may have evolved according to the public future region relation (defined below).
The \emph{private future world} relation $W' \futurestr W$ is defined similarly,
using a private future region relation.

@@

% Notice that the public future region relation is a subset of the
% private future region relation.

@@

\section{Examples}
\label{sec:examples}
In this section, we demonstrate how our formalization of capability
safety allows us to prove local-state encapsulation and control-flow
correctness properties for challenging program examples. The security
measures of Section~\ref{sec:stack-and-return-pointer} are deployed to
ensure these properties. Since we are dealing with assembly language,
there are many details to the formal treatment, and therefore we
necessarily have to omit some details in the lemmas we state here. The
examples may look deceivingly short, but it is because they use the
previously described macro instructions, which expands to multiple basic instructions. The examples would be unintelligible without the macros. The interested
reader can find all the technical details in the technical
appendix~\citep{technical_appendix}.

@@

For our purposes, this restriction is unproblematic, since we are only
interested in proving semantic properties (e.g., an assertion will never fail).
However, in other situations, we may be interested in proving more syntactic
properties like the more syntactic properties, that are often considered in
object capability literature like confinement, no authority amplification etc.
Although such properties are typically more restrictive and less easy to use for
reasoning, \citet{Devriese:2016ObjCap} have demonstrated how a logical relation
much like ours can be adapted to also support them, by quantifying the logical
relation over a custom interpretation of effectful computations and the type of
references. We expect their solution can be readily adapted to our setting,
modulo some details (like the fact that we do not just have read-write
capabilities, but also other types).\\\\

% \emph{No program logic} TODO: discuss this?
